Rule-Based Normalization of German Twitter Messages

### 2013-08-16 darmstadt_gscl_2013/article_twitter_normalization.tex
srticle updated

As can be seen from the figures, both kinds of spelling variations
have nearly Zipfian distribution. However colloquial spelling
variants, if used, tend to be used frequently whereas non-colloquial
misspellings are rather represented by sporadic singletons. This could
be explained by the fact that colloquial spellings are usually formed
by systematic rewriting processes which are also usually applied to
frequently used words. True misspellings, on the contrary, are rather
produced by occasional slips of the finger, so they neither have an
apparent system in them nor they tend to reoccur in text.

In order to investigate which processes were the most common sources
of colloquial spellings

These processes are supposed to make written form of words more
similar to their casual soundings in everyday speech.

According to our data, the most productive of such
processes were:
\begin{itemize}
  \item Omissions of `e' in unstressed (``schwa'') positions,
    e.g. \textit{w\"urd}, \textit{zuguckn} etc. In cases when `e' was part of
    the impersonal pronoun ``es'' following a verb, remaining `s' of this
    pronoun was usually appended to the preceding verb form;

  \item Complete omissions or replacements of final consonants with their
    voiceless equivalents, e.g. \textit{nich} instead of \textit{nicht} or
    \textit{Tach} instead of \textit{Tag};

>>>>

As can be seen from the figures, both kinds of spelling variations
have nearly Zipfian distribution. However colloquial spelling
variants, if used, tend to be used frequently whereas non-colloquial
misspellings are rather represented by sporadic singletons. This could
be explained by the fact that colloquial spellings are usually formed
by systematic rewriting processes which are also normally applied to
frequently used words. True misspellings, on the contrary, are rather
produced by occasional slips of the finger, so they neither have an
apparent system in them nor they tend to reoccur in text.

On closer examination of colloquial spellings, it could be found that
a large part of them was a result of phonetically motivated
rewritings.

According to our data, the most productive of such slang producing
processes turned out to be:
\begin{itemize}
  \item Omission of `e' in unstressed positions, e.g. \textit{w\"urd},
    \textit{zuguckn} etc. In cases when `e' was part of the impersonal
    pronoun ``es'' following a verb, the remaining `s' of this pronoun
    was usually appended to the preceding verb form,
    e.g. \textit{wirds} instead of \textit{wird es};

  \item Complete omission or replacement of final consonants with
    their voiceless equivalents, e.g. \textit{nich} instead of
    \textit{nicht} or \textit{Tach} instead of \textit{Tag};
